My title

### 2024-04-13 paper/paper.qmd
Added data graphs

library(tidyverse)
```

@@

>>>>

library("tidyverse")
library("arrow")
library("here")
library("knitr")
library("kableExtra")

clean_anime <- read_parquet(here::here("data/analysis_data/clean_anime.parquet"))
```

@@

## Top 10000 Ranked Anime

```{r, echo=FALSE}
#| label: tbl-anime_dataset
#| tbl-cap: Sample of Anime
head(clean_anime, 5) %>% 
  kable(
    booktabs = TRUE,
    linesep = ""
  ) %>% kable_styling(latex_options = "scale_down")
```

```{r, echo=FALSE}
#| label: fig-score_distribution
#| fig-cap: Distribution of scores of top 10000 anime

mean_score <- mean(clean_anime$mean)

clean_anime %>%
  ggplot(aes(x = mean)) +
  geom_histogram(binwidth = 0.1, color="darkblue", fill="lightblue") +
  theme_minimal() +
  geom_vline(aes(xintercept=mean_score), linetype="dashed", size=1) +
  annotate("text", x = mean_score + 0.1, y = 550, label = paste("Mean Score:", round(mean_score, 2)), 
           hjust = 0, vjust = -1) +
  labs(x = "Score", y = "count", title = "Distribution of scores of top 10000 anime")
```

```{r, echo=FALSE}
#| label: fig-rank_vs_popularity
#| fig-cap: Rank vs Popularity

clean_anime |>  ggplot(aes(x = rank, y = popularity)) +
  geom_point(color = "blue", size=0.5) +
  labs(x = "Rank (Low to High)", y = "Popularity (Low to High)", title = "Rank vs Popularity") +
  scale_x_reverse() +
  scale_y_reverse() +
  theme_minimal()
```
